Resurgence of the Airy function

### 2022-01-10 airy-resurgence.tex
Add figures for contour argument

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
%%\usepackage{amsthm}

@@

\begin{document}
\maketitle
\section{The Laplace transform}
\subsection{Analytic version}
\subsubsection{Regularity and decay properties}\label{reg-decay}
Take two copies $\R$ and $\hat{\R}$ of the real line, with standard coordinates $z$ and $\zeta$ respectively. The Laplace transform in $\zeta$ turns a function $\hat{\varphi}$ on $\hat{\R}_{\zeta > 0}$ into a function $\laplace_\zeta \hat{\varphi}$ on $\R_{z > 0}$, defined by the integral
\[ \laplace_\zeta \hat{\varphi} = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta. \]
For $a \in [0, \infty]$, recall that recall that $O_{\zeta \to a}(g)$ is the space of functions $\varphi$ on $\hat{\R}_{\zeta > 0}$ with $|\varphi| \lesssim g$ in some neighborhood of $a$. A function is {\em subexponential} if it's in $O_{\zeta \to \infty}(e^{c\zeta})$ for all $c > 0$. Let $\mathcal{E}_\zeta$ be the space of subexponential functions on $\hat{\R}_{\zeta > 0}$ which are $L^1$ both locally and around $\zeta = 0$. If $\hat{\varphi}$ is in $\mathcal{E}_\zeta$, then $\varphi = \laplace_\zeta \hat{\varphi}$ is well-defined, and it extends to a holomorphic function on the right half-plane $\hat{\C}_{\Re(z) > 0}$~\cite[\S 5.6]{diverg-resurg-i}. If $\hat{\varphi}$ is in $O_{\zeta \to 0}(1)$, then $\varphi$ is in $O_{z \to \infty}(z^{-1})$~\cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality. For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if $\hat{\varphi}$ is in $O_{\zeta \to 0}(\zeta^{\alpha})$, with $\alpha > -1$, then $\varphi$ is in $O_{z \to \infty}\big(z^{-(\alpha + 1)}\big)$.
\subsubsection{Action on differential operators}\label{L-diff-op}
When $\hat{\varphi} \in \mathcal{E}_\zeta$, we can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}\label{id:L-mult}
\laplace_\zeta (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \hat{\varphi}.
\end{equation}

@@

Define new coordinates $x$ and $\xi$ on $\R$ and $\hat{\R}$, respectively, so that $\zeta = b\xi$ and $z\,d\zeta = x\,d\xi$. Explicitly, $z = b^{-1}x$. From the calculation
\begin{align*}
\laplace_\zeta \hat{\varphi} & = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
& = \int_0^\infty e^{-x\xi}\,\hat{\varphi}\;b\,d\xi \\
& = b \laplace_\xi \hat{\varphi},
\end{align*}
we learn that
\[ \laplace_\xi \hat{\varphi} = b^{-1} \laplace_\zeta \hat{\varphi}. \]
\section{The Airy equation}
\subsection{Basics}
The Airy equation is
\begin{equation}\label{eqn:airy}
\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \psi = 0.
\end{equation}
One solution is given by the Airy function,
\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma_0} \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
where $\Gamma_0$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$. With the substitution $t = -2uy^{1/2}$, we can rewrite the Airy integral as
\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{-y^{-1/2} \Gamma_0} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
\subsection{Rewriting as a modified Bessel equation}
We can distill the most interesting part of the Airy function by writing
\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\, K\big(\tfrac{2}{3} y^{3/2}\big), \]
where
\[ K(z) = \frac{\sqrt{3}}{i} \int_{-z^{-1/3}\Gamma_0} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du. \]
Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
\begin{equation}\label{eqn:mod-bessel}
\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
\end{equation}
In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.

@@

\subsection{Going to the spatial domain}

@@

\subsubsection{Success at $\zeta = 1$}

@@

Following this plan, let's find $\hat{K}$ explicitly. Defining another coordinate $\xi$ on $\hat{\R}$ so that $\zeta_1 = -2\xi$, we can rewrite equation~\ref{eqn:shifted-spatial-mod-bessel} as the hypergeometric equation
\begin{equation}\label{eqn:hypergeom}
\left[\xi(1 - \xi) \big(\tfrac{\partial}{\partial \xi}\big)^2 + 3(\tfrac{1}{2} - \xi) \tfrac{\partial}{\partial \xi} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0.
\end{equation}
%With the change of variable $\xi = \tfrac{1}{2}(1-\zeta)$, equation~\ref{eqn:spatial-mod-bessel} becomes the hypergeometric equation
The hypergeometric function
\[ \hat{f}_1 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
satisfies equation~\ref{eqn:hypergeom} by definition. It's not the solution we want, though, because it's holomorphic around $\xi = 0$. Formula~15.10.12 from \cite{dlmf} gives another solution,
\[ \hat{f}_0 = \xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big), \]
which is a holomorphic multiple of $\xi^{-1/2}$ near $\xi = 0$. By the argument above, $f_0 = \laplace_{\zeta_1} \hat{f}_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}. This suggests that a constant multiple of $\hat{f}_0$ is our desired $\hat{K}$. The power series~\cite[equation~15.2.1]{dlmf}
\[ \hat{f}_0 = \xi^{-1/2} + \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{(\tfrac{1}{2})_1 \; 1!}\;\xi^{1/2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{(\tfrac{1}{2})_2 \; 2!}\;\xi^{3/2} + \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{(\tfrac{1}{2})_3 \; 3!}\;\xi^{5/2} + \ldots \]
converges near $\xi = 0$, showing that
\[ \hat{f}_0 \in \xi^{-1/2} + O_{\xi \to 0}(\xi^{1/2}). \]
In terms of $\zeta_1$, we have
\[ \hat{f}_0 \in -i \sqrt{2}\,\zeta_1^{-1/2} + O_{\zeta_1 \to 0}(\zeta_1^{1/2}). \]
%%Using DLMF~15.10.13, we can see that
%%\[ \hat{f}_0 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
%%also satisies equation~\ref{eqn:hypergeom}.
%%-------------------------------------------------------------
%%By DLMF~15.10.17,
%%\[ \hat{f}_0 = \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{4}{3})}\;\xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) + \frac{\Gamma(-\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}\;\hat{f}_1. \]
%%The coefficients simplify to
%%\begin{align*}
%%\sqrt{\pi}\;\big(\tfrac{1}{2}\sqrt{\pi}\big)\;\frac{\sin(\tfrac{2}{3} \pi)}{\pi} & = \frac{\sqrt{3}}{4} \\
%%\big({-2}\sqrt{\pi}\big) \big(\tfrac{1}{2}\sqrt{\pi}\big)\;\frac{\sin(\tfrac{1}{6} \pi)}{\pi} & = -\frac{1}{2}
%%\end{align*}
%%respectively, giving
Using the decay properties from Section~\ref{reg-decay}, we deduce that
\[ f_0 \in -i \sqrt{2\pi}\,z^{-1/2} + O_{z \to \infty}(z^{-3/2}). \]
Since we know that $f_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}, this confirms that $f_0$ is a constant multiple of $\kappa$, which is the only subexponential solution of equation~\ref{eqn:shifted-mod-bessel} (up to scaling). Comparing with series~\ref{bessel-asymp}, we see that $\kappa = i\,\tfrac{1}{2}\,f_0$. We conclude that $\kappa = \laplace_{\zeta_1} \hat{K}$ for
\[ \hat{K} = \tfrac{1}{\sqrt{2}}\,\zeta_1^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
\section{Sketches}
\subsection{Contour argument}
The hypergeometric function
\[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
satisfies equation~\ref{eqn:hypergeom} by definition. It has a singularity of type $(1 - \xi)^{-1/2}$ at $\xi = 1$, and continues holomorphically to the rest of $\hat{\C}$.

Based on the calculations in the other sheet, we should have
\[ K(z) = i \frac{2}{\sqrt{3}} \int_{\text{Hankel at } 1} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
This is because the hypergeometric function in the integrand happens to be algebraic. It can be expressed in terms of Legendre functions and rearranged to get
\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \frac{1}{4u^2 - 1} \]
with $\zeta = -4u^3 + 3u$.

The quadratic transformation identity DLMF~15.8.27 then shows that
\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) \propto F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) + F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big), \]
so we have
\[ K(z) \propto \int_{\text{Hankel at } 1} e^{-z\zeta} \big[F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) + F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)\big]\;d\zeta. \]
The first term in the integrand is regular on $\zeta \in [1, \infty)$, so it integrates to zero. The second term looks like $(1 - \zeta)^{-1/2}$ times a function which is regular for $\zeta \in [1, \infty)$, so integrating it along a Hankel contour is the same as integrating it times two times a direct contour, with its value continued from below the singularity. Hence,
\[ K(z) \propto \int^\infty_1 e^{-z\zeta} F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)\;d\zeta. \]
With $\zeta = 1 + \tilde{\zeta}$, we get $1 - \xi = 1 + \tfrac{1}{2} \tilde{\zeta}$, so
\begin{align*}
K(z) & = \int^\infty_0 e^{-z(1 + \tilde{\zeta})} F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\tilde{\zeta}\big)\;d\tilde{\zeta} \\
e^z K(z) & = \int^\infty_0 e^{-z\tilde{\zeta}} F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\tilde{\zeta}\big)\;d\tilde{\zeta}
\end{align*}
In other words, $\kappa(z) = e^z K(z)$ is the Laplace transform of $\hat{\kappa}(\tilde{\zeta}) = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\tilde{\zeta}\big)$. We've confirmed numerically that $\hat{\kappa}(\tilde{\zeta})$ seems to have a singularity of type $\tilde{\zeta}^{-1/2}$ at $\tilde{\zeta} = 0$, as expected. \textbf{Can we see this analytically?}

Using the DLMF identities 15.10.12 and 15.10.14, we can see that the functions
\begin{align*}
\xi^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) \\
(1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big)
\end{align*}
also satisfy equation~\ref{eqn:hypergeom}. Numerically, these functions appear to sum to a constant multiple of $F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)$.
\subsection{Correspondence with Mari\~{n}o's series}
Let $f_1(z)$ be the holomorphic function corresponding to Mari\~{n}o's formal power series $\varphi_1(z^{-1})$. The formal power series corresponding to $f$ will be written in the variable $z$.

>>>>

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
%%\usepackage{amsthm}
\usepackage{graphicx}

@@

\begin{document}
\maketitle
\section{The Laplace transform}
\subsection{Analytic version}
\subsubsection{Regularity and decay properties}\label{reg-decay}
Take two copies $\R$ and $\hat{\R}$ of the real line, with standard coordinates $z$ and $\zeta$ respectively. The Laplace transform in $\zeta$ turns a function $\hat{\varphi}$ on $\hat{\R}_{\zeta > 0}$ into a function $\laplace_\zeta \hat{\varphi}$ on $\R_{z > 0}$, defined by the integral
\[ \laplace_\zeta \hat{\varphi} = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta. \]
For $a \in [0, \infty]$, recall that recall that $O_{\zeta \to a}(g)$ is the space of functions $\varphi$ on $\hat{\R}_{\zeta > 0}$ with $|\varphi| \lesssim g$ in some neighborhood of $a$. A function is {\em subexponential} if it's in $O_{\zeta \to \infty}(e^{c\zeta})$ for all $c > 0$. Let $\mathcal{E}_\zeta$ be the space of subexponential functions on $\hat{\R}_{\zeta > 0}$ which are $L^1$ both locally and around $\zeta = 0$. If $\hat{\varphi}$ is in $\mathcal{E}_\zeta$, then $\varphi = \laplace_\zeta \hat{\varphi}$ is well-defined, and it extends to a holomorphic function on the right half-plane $\C_{\operatorname{Re}(z) > 0}$~\cite[\S 5.6]{diverg-resurg-i}. If $\hat{\varphi}$ is in $O_{\zeta \to 0}(1)$, then $\varphi$ is in $O_{z \to \infty}(z^{-1})$~\cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality. For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if $\hat{\varphi}$ is in $O_{\zeta \to 0}(\zeta^{\alpha})$, with $\alpha > -1$, then $\varphi$ is in $O_{z \to \infty}\big(z^{-(\alpha + 1)}\big)$.
\subsubsection{Action on differential operators}\label{L-diff-op}
When $\hat{\varphi} \in \mathcal{E}_\zeta$, we can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}\label{id:L-mult}
\laplace_\zeta (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \hat{\varphi}.
\end{equation}

@@

Define new coordinates $x$ and $\xi$ on $\R$ and $\hat{\R}$, respectively, so that $\zeta = b\xi$ and $z\,d\zeta = x\,d\xi$. Explicitly, $z = b^{-1}x$. From the calculation
\begin{align*}
\laplace_\zeta \hat{\varphi} & = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
& = \int_0^\infty e^{-x\xi}\,\hat{\varphi}\;b\,d\xi \\
& = b \laplace_\xi \hat{\varphi},
\end{align*}
we learn that
\[ \laplace_\xi \hat{\varphi} = b^{-1} \laplace_\zeta \hat{\varphi}. \]
\section{The Airy equation}
\subsection{Basics}
The Airy equation is
\begin{equation}\label{eqn:airy}
\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \psi = 0.
\end{equation}
One solution is given by the Airy function,
\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma} \exp\left(-\tfrac{1}{3}t^3 + yt\right)\,dt, \]
where $\Gamma$ is a path that comes from $\infty$ at $120^\circ$ and goes to $\infty$ at $-120^\circ$.
\begin{center}
\includegraphics{figures/u_contour.pdf} \\[1em]
{\small The contour $\Gamma$ in the $u$ plane.}
\end{center}
With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Gamma} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
\subsection{Rewriting as a modified Bessel equation}
We can distill the most interesting part of the Airy function by writing
\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\, K\big(\tfrac{2}{3} y^{3/2}\big), \]
where
\begin{equation}\label{integral:mod-bessel}
K(z) = \frac{\sqrt{3}}{i} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
\end{equation}
Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
\begin{equation}\label{eqn:mod-bessel}
\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
\end{equation}
In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.

@@

\subsection{Going to the spatial domain}\label{spatial}

@@

\subsubsection{Success at $\zeta = 1$}\label{spatial-success}

@@

Following this plan, let's find $\hat{K}$ explicitly. Defining another coordinate $\xi$ on $\hat{\R}$ so that $\zeta_1 = -2\xi$, we can rewrite equation~\ref{eqn:shifted-spatial-mod-bessel} as the hypergeometric equation
\begin{equation}\label{eqn:hypergeom}
\left[\xi(1 - \xi) \big(\tfrac{\partial}{\partial \xi}\big)^2 + 3(\tfrac{1}{2} - \xi) \tfrac{\partial}{\partial \xi} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0.
\end{equation}
The hypergeometric function
\[ \hat{g}_1 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
satisfies equation~\ref{eqn:hypergeom} by definition. It's not the solution we want, though, because it's holomorphic around $\xi = 0$. Formula~15.10.12 from \cite{dlmf} gives another solution,
\[ \hat{f}_0 = \xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big), \]
which is a holomorphic multiple of $\xi^{-1/2}$ near $\xi = 0$. By the argument above, $f_0 = \laplace_{\zeta_1} \hat{f}_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}. This suggests that a constant multiple of $\hat{f}_0$ is our desired $\hat{K}$. The power series~\cite[equation~15.2.1]{dlmf}
\[ \hat{f}_0 = \xi^{-1/2} + \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{(\tfrac{1}{2})_1 \; 1!}\;\xi^{1/2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{(\tfrac{1}{2})_2 \; 2!}\;\xi^{3/2} + \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{(\tfrac{1}{2})_3 \; 3!}\;\xi^{5/2} + \ldots \]
converges near $\xi = 0$, showing that
\[ \hat{f}_0 \in \xi^{-1/2} + O_{\xi \to 0}(\xi^{1/2}). \]
In terms of $\zeta_1$, we have
\[ \hat{f}_0 \in -i \sqrt{2}\,\zeta_1^{-1/2} + O_{\zeta_1 \to 0}(\zeta_1^{1/2}). \]
Using the decay properties from Section~\ref{reg-decay}, we deduce that
\[ f_0 \in -i \sqrt{2\pi}\,z^{-1/2} + O_{z \to \infty}(z^{-3/2}). \]
Since we know that $f_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}, this confirms that $f_0$ is a constant multiple of $\kappa$, which is the only subexponential solution of equation~\ref{eqn:shifted-mod-bessel} (up to scaling). Comparing with series~\ref{bessel-asymp}, we see that $\kappa = i\,\tfrac{1}{2}\,f_0$. We conclude that $\kappa = \laplace_{\zeta_1} \hat{K}$ for
\[ \hat{K} = \tfrac{1}{\sqrt{2}}\,\zeta_1^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
\section{Sketches}
\subsection{Contour argument}
We can recast integral~\ref{integral:mod-bessel} into $\hat{\C}$ by setting $\zeta = 4u^3 - 3u$. Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in $\hat{\C}$ and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
\begin{equation}\label{integral:mod-bessel-zeta}
K(z) = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
\end{equation}
For $z \in (0, \infty)$, the contour $\gamma(z)$ runns clockwise around $[1, \infty)$, as shown below. Let's assume $z \in (0, \infty)$ for the rest of the section. \textbf{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
\begin{center}
\includegraphics{figures/zeta_contour.pdf} \\[1em]
{\small The contour $\gamma_1$ in $\hat{\C}$.}
\end{center}

It happens\footnote{How to verify this? This hypergeometric function can be written in terms of Legendre functions, but I don't know where to go from there.} that for our desired branch of $u$,
\[ \frac{1}{4u^2 - 1} = F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
so we can rewrite integral~\ref{integral:mod-bessel-zeta} as
\[ K(z) = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.

In addition to the solutions $\hat{g}_1$ and $\hat{f}_0$ from Section~\ref{spatial-success}, equation~\ref{eqn:hypergeom} has the solutions
\begin{alignat*}{2}
\hat{g}_0 &\;=\;& & F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big) \\
\hat{f}_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big),
\end{alignat*}
given by formulas 15.10.13 and 15.10.14 from \cite{dlmf}. These four solutions are related by identities 15.10.18, and 15.10.22 from \cite{dlmf}:
\begin{alignat*}{3}
\hat{f}_1 &\;=\;&\tfrac{1}{\sqrt{3}}\,\hat{g}_1 &\;+\;& \tfrac{1}{2}\,\hat{f}_0 \\
\hat{f}_0 &\;=\;& \tfrac{1}{\sqrt{3}}\,\hat{g}_0 &\;+\;& \tfrac{1}{2}\,\hat{f}_1.
\end{alignat*}
Summing these identities, we see that
\[ \hat{g}_1 + \hat{g}_0 = \tfrac{\sqrt{3}}{2}\,(\hat{f}_1 + \hat{f}_0). \]

The quadratic transformation identity 15.8.27 from \cite{dlmf} shows that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
\begin{align*}
F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) & = \tfrac{1}{3}(\hat{g}_1 + \hat{g}_0) \\
& = \tfrac{1}{2\sqrt{3}}(\hat{f}_1 + \hat{f}_0)
\end{align*}
so we have
\[ K(z) = \frac{1}{6i} \int_{\gamma_z} e^{-z\zeta} (\hat{f}_1 + \hat{f}_0)\;d\zeta. \]
The solution $\hat{f}_1$ is regular on $\zeta \in [1, \infty)$, so it integrates to zero. The solution $\hat{f}_0$ looks like $(1 - \zeta)^{-1/2}$ times a function which is regular on $\zeta \in [1, \infty)$, so integrating it along $\gamma_z$ is the same as integrating it negative-twice along the contour that goes rightward from $1$, with its value continued from above the singularity. Hence,
\begin{align*}
K(z) & = \frac{i}{3} \int^\infty_1 e^{-z\zeta} \hat{f}_0\;d\zeta \\
& = \tfrac{i}{3} \laplace_{\zeta_1} \hat{f}_0.
\end{align*}
\textbf{[Constant conflicts with Section~\ref{spatial}]}
\subsection{Correspondence with Mari\~{n}o's series}
Let $f_1(z)$ be the holomorphic function corresponding to Mari\~{n}o's formal power series $\varphi_1(z^{-1})$. The formal power series corresponding to $f$ will be written in the variable $z$.
